### 2016-09-02 ms/ms/ms.tex
cppp function working

\begin{abstract}  
  \begin{enumerate}
  \item occupancy models are everywhere, but model fitting and
    assessment are extrememly computationally intensive
  \item Using the NIMBLE package for R, we develop combined
    computational approaches to improve computational efficiency
    including user defined and automatic blocking of parameters for
    MCMC, filtering over latent states, and customized MCMC samplers
    for specific parameters. We test these approaches for three
    representative occupancy models of varying levels of complexity
    including a single species dynamic (i.e., multi-season) model with
    spatial auto correlation, and a mutli-species model. We also use
    calibrated posterior $p$-values to assess model fit.
  \item These computation approaches lead to an improvement in MCMC
    sampling efficiency, particularly with the more complex,
    mutli-species model.
  \item Ours results highlight the need for more customizable
    approaches to MCMC to fit and assess hierachical models in order
    to ensure occupancy models are accessible to practitioners. By
    implementing MCMC procedures and model assessment techniques open
    source software, we have made progress toward tis aim.
  \item \textit{Implications:}
  \end{enumerate}
\end{abstract}

>>>>

\begin{abstract}  
  \begin{enumerate}
  \item occupancy models are everywhere, but model fitting and
    assessment are extrememly computationally intensive
  \item Using the NIMBLE package for R, we develop combined
    computational approaches to improve computational efficiency
    including user defined and automatic blocking of parameters for
    MCMC, filtering over latent states, and customized MCMC samplers
    for specific parameters. We test these approaches using three
    representative occupancy models of varying levels of complexity
    including a single species dynamic (i.e., multi-season) model with
    spatial auto correlation, and a mutli-species model. We also use
    calibrated posterior $p$-values to assess model fit.
  \item These computation approaches lead to an improvement in MCMC
    sampling efficiency, particularly with the more complex,
    mutli-species model.
  \item Ours results highlight the need for more customizable
    approaches to MCMC to fit and assess hierachical models in order
    to ensure occupancy models are accessible to practitioners. By
    implementing MCMC procedures and model assessment techniques open
    source software, we have made progress toward this aim.
  \item \textit{Implications:}
  \end{enumerate}
\end{abstract}
